---
title: "Urbanization influences communities of milkweed-specialist herbivorous insects"
subtitle: "ON_herb pSEM Checking"
author:
  - Lindsay S. Miles
  - Vanessa J. Nahn
  - David Murray-Stoker
  - Marc T. J. Johnson
output:
  pdf_document:
    toc: true
    toc_depth: 4
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Package for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```

```{r Load Packages, include = FALSE}
## Load packages for data management and analysis
library(broom)
library(easystats)
library(MASS)

## Load the tidyverse
library(tidyverse)
```





\newpage
# Background & Questions

We examined how urbanization could disrupt specialized plant-herbivores species interactions, comparing responses by different cities and by traits of the herbivore species. We surveyed arthropod communities in the early and late growing season of the common milkweed (*Asclepias syriaca*) across six cities in southern Ontario (Fig. 1).

We asked the following five questions: **CHECK THESE**

(Q1) Is insect herbivore species diversity, total abundance, and leaf herbivory lower in urban compared to rural habitats?
(Q2) Does arthropod community composition vary between urban and rural habitats?
(Q3) Does the response of the herbivore community vary with city size?
(Q4) Does dispersal ability of insect species influence individual species’ responses to urbanization?
(Q5) How does urbanization influence interactions among herbivore species? 

Here, **PROVIDE SHORT DESCRIPTION ABOUT PSEM MODEL CHECKING**




\newpage
# Data Management


```{r Load Data, echo = TRUE}
## Read in data
raw.SEM.data <- read_csv(
	"data/toronto_herbivores.csv",
	col_types = c("ffffnfiiiiiiiiii"),
	show_col_types = FALSE
	) %>%
	unique()

## Extract site info from the raw data
site.info <- raw.SEM.data %>%
  select(Population, Season, Distance) %>%
	unique()
```



\newpage
## Abundance Data

```{r Abundance Data Management: Aggregation, include = FALSE}
## Sum herbivore abundances from all 5 plants by season and  population
# Danaus
danaus.abundances <- raw.SEM.data %>%
  select(Danaus)

# Rhyssomatus
rhyssomatus.abundances <- raw.SEM.data %>%
  select(Rhyssomatus)

# Aphis
aphis.abundances <- raw.SEM.data %>%
  select(Aphis)

# Tetraopes
tetraopes.abundances <- raw.SEM.data %>%
  select(Tetraopes)

# Liriomyza
liriomyza.abundances <- raw.SEM.data %>%
  select(Liriomyza)
```

\vspace{10pt}

```{r Abundance Data Management: Merging, echo = TRUE, results = "hide"}
## Select site info and focal herbivores
abundance.data <- raw.SEM.data %>%
	select(Population, Season, Distance, Danaus, Rhyssomatus, Aphis, Tetraopes, Liriomyza)

## Subset early data
early.abundances <- abundance.data %>%
  filter(Season == "Early") %>%
  rename(
    Danaus.early = Danaus, Rhyssomatus.early = Rhyssomatus, Aphis.early = Aphis,
    Tetraopes.early = Tetraopes, Liriomyza.early = Liriomyza
  )

## Remove season column
early.abundances <- early.abundances[, -2]

## Subset late data
late.abundances <- abundance.data %>%
  filter(Season == "Late") %>%
  rename(
    Danaus.late = Danaus, Rhyssomatus.late = Rhyssomatus, Aphis.late = Aphis,
    Tetraopes.late = Tetraopes, Liriomyza.late = Liriomyza
  )

## Remove season column
late.abundances <- late.abundances[, -2]

## Merge early and late info final abundance dataframe
final.abundance.data <- early.abundances %>%
  left_join(late.abundances) %>%
  na.omit()
```



\newpage
## Presence-Absence Data

```{r Presence-Absence Data: Aggregation, echo = TRUE}
## Convert abundance matrices to presence-absence matrices
# Danaus
danaus.presabs <- danaus.abundances
danaus.presabs[danaus.presabs > 0] <- 1
danaus.presabs.binary <- cbind(site.info, danaus.presabs)

# Rhyssomatus
rhyssomatus.presabs <- rhyssomatus.abundances
rhyssomatus.presabs[rhyssomatus.presabs > 0] <- 1
rhyssomatus.presabs.binary <- cbind(site.info, rhyssomatus.presabs)

# Aphis
aphis.presabs <- aphis.abundances
aphis.presabs[aphis.presabs > 0] <- 1
aphis.presabs.binary <- cbind(site.info, aphis.presabs)

# Tetraopes
tetraopes.presabs <- tetraopes.abundances
tetraopes.presabs[tetraopes.presabs > 0] <- 1
tetraopes.presabs.binary <- cbind(site.info, tetraopes.presabs)

# Liriomyza
liriomyza.presabs <- liriomyza.abundances
liriomyza.presabs[liriomyza.presabs > 0] <- 1
liriomyza.presabs.binary <- cbind(site.info, liriomyza.presabs)
```

\vspace{10pt}

```{r Presence-Absence Data: Merging, echo = TRUE, results = "hide"}
## Bind herbivore presence-absence together
herbivore.presabs <- danaus.presabs.binary %>%
  left_join(rhyssomatus.presabs.binary) %>%
  left_join(aphis.presabs.binary) %>%
  left_join(tetraopes.presabs.binary) %>%
  left_join(liriomyza.presabs.binary)

## Merge site info with presence-absence data
presence.absence.data <- site.info %>%
  full_join(herbivore.presabs)

## Subset early data
early.presence.absence <- presence.absence.data %>%
  filter(Season == "Early") %>%
  rename(
    Danaus.early = Danaus, Rhyssomatus.early = Rhyssomatus,
    Aphis.early = Aphis, Tetraopes.early = Tetraopes,
    Liriomyza.early = Liriomyza
  )

## Remove season column
early.presence.absence <- early.presence.absence[, -2]

## Subset late data
late.presence.absence <- presence.absence.data %>%
  filter(Season == "Late") %>%
  rename(
    Danaus.late = Danaus, Rhyssomatus.late = Rhyssomatus,
    Aphis.late = Aphis, Tetraopes.late = Tetraopes,
    Liriomyza.late = Liriomyza
  )

## Remove season column
late.presence.absence <- late.presence.absence[, -2]

## Merge early and late info final presence-absence dataframe
final.presence.absence.data <- early.presence.absence %>%
  left_join(late.presence.absence) %>%
  na.omit()
```


```{r Save the pSEM Data, include = FALSE}
save.image("data_analysis/1-analyses/pSEM_data.RData")
```



\newpage
# Model Fitting & Diagnostics

*UPDATE*

Prior to fitting the pSEMs, each individual model was fitted and assumptions were visually inspected using the DHARMa package. Models were fitted for both abundance and presence-absence data. Abundance models were fitted using GLMs with a Poisson distribution and log-link function or negative binomial GLMs to account for overdispersion, while presence-absence models were fitted using GLMs with a binomial distribution and logit-link function.



\newpage
## Urbanization (Hypothesized pSEM 1) | Abundance

```{r Urbanization Structural Equation Fitting (Abundance), echo = TRUE}
## Danaus
danaus.abundance.early.urb.toronto <- glm.nb(
	Danaus.early ~ Distance,
	data = final.abundance.data
	)
danaus.abundance.late.urb.toronto <- glm.nb(
	Danaus.late ~ Distance,
  data = final.abundance.data
	)

## Rhyssomatus
rhyssomatus.abundance.early.urb.toronto <- glm.nb(
	Rhyssomatus.early ~ Distance,
  data = final.abundance.data
	)
rhyssomatus.abundance.late.urb.toronto <- glm.nb(
	Rhyssomatus.late ~ Distance,
  data = final.abundance.data
	)

## Aphis
aphis.abundance.early.urb.toronto <- glm.nb(
	Aphis.early ~ Distance,
  data = final.abundance.data
	)
aphis.abundance.late.urb.toronto <- glm.nb(
	Aphis.late ~ Distance,
  data = final.abundance.data
	)

## Tetraopes
tetraopes.abundance.early.urb.toronto <- glm.nb(
	Tetraopes.early ~ Distance,
  data = final.abundance.data
	)
tetraopes.abundance.late.urb.toronto <- glm.nb(
	Tetraopes.late ~ Distance,
  data = final.abundance.data
	)

## Liriomyza
liriomyza.abundance.early.urb.toronto <- glm.nb(
	Liriomyza.early ~ Distance,
  data = final.abundance.data
	)
liriomyza.abundance.late.urb.toronto <- glm.nb(
	Liriomyza.late ~ Distance,
  data = final.abundance.data
	)
```

\vspace{10pt}

```{r Urbanization Structural Equation Diagnostics (Abundance), echo = TRUE, eval = FALSE}
## Check model assumptions
# Danaus abundance GLMs
check_model(danaus.abundance.early.urb.toronto) # Decent fit
check_model(danaus.abundance.late.urb.toronto) # Decent fit

# Rhyssomatus abundance GLMs
check_model(rhyssomatus.abundance.early.urb.toronto) # Good fit
check_model(rhyssomatus.abundance.late.urb.toronto) # Good fit

# Aphis abundance GLMs
check_model(aphis.abundance.early.urb.toronto) # Good fit
check_model(aphis.abundance.late.urb.toronto) # Good fit

# Tetraopes abundance GLMs
check_model(tetraopes.abundance.early.urb.toronto) # Decent fit
check_model(tetraopes.abundance.late.urb.toronto) # Poor fit

# Liriomyza abundance GLMs
check_model(liriomyza.abundance.early.urb.toronto) # Good fit
check_model(liriomyza.abundance.late.urb.toronto) # Good fit
```



\newpage
## Herbivore Interactions (Hypothesized pSEM 2) | Abundance

```{r Herbivore Interactions Structural Equation Fitting (Abundance), echo = TRUE}
## Danaus
danaus.abundance.early.herb.toronto <- glm.nb(
	Danaus.early ~ Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
	data = final.abundance.data
	)
danaus.abundance.late.herb.toronto <- glm.nb(
	Danaus.late ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)

## Rhyssomatus
rhyssomatus.abundance.late.herb.toronto <- glm.nb(
	Rhyssomatus.late ~ Rhyssomatus.early,
  data = final.abundance.data
	)

## Aphis
aphis.abundance.early.herb.toronto <- glm.nb(
	Aphis.early ~ Danaus.early + Rhyssomatus.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)
aphis.abundance.late.herb.toronto <- glm.nb(
	Aphis.late ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)

## Tetraopes
tetraopes.abundance.early.herb.toronto <- glm.nb(
	Tetraopes.early ~ Danaus.early + Rhyssomatus.early + Aphis.early + Liriomyza.early,
  data = final.abundance.data
	)
tetraopes.abundance.late.herb.toronto <- glm.nb(
	Tetraopes.late ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)

## Liriomyza
liriomyza.abundance.early.herb.toronto <- glm.nb(
	Liriomyza.early ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early,
  data = final.abundance.data
	)
liriomyza.abundance.late.herb.toronto <- glm.nb(
	Liriomyza.late ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)
```

\vspace{10pt}

```{r Herbivore Interactions Structural Equation Diagnostics (Abundance), echo = TRUE, eval = FALSE}
## Check model assumptions
# Danaus abundance GLMs
check_model(danaus.abundance.early.herb.toronto) # Good fit
check_model(danaus.abundance.late.herb.toronto) # Good fit

# Rhyssomatus abundance GLMs
check_model(rhyssomatus.abundance.late.herb.toronto) # Good fit

# Aphis abundance GLMs
check_model(aphis.abundance.early.herb.toronto) # Good fit
check_model(aphis.abundance.late.herb.toronto) # Good fit

# Tetraopes abundance GLMs
check_model(tetraopes.abundance.early.herb.toronto) # Decent fit
check_model(tetraopes.abundance.late.herb.toronto) # Poor fit

# Liriomyza abundance GLMs
check_model(liriomyza.abundance.early.herb.toronto) # Good fit
check_model(liriomyza.abundance.late.herb.toronto) # Good fit
```



\newpage
## Urbanization & Herbivore Interactions (Hypothesized pSEM 3) | Abundance

```{r Urbanization + Herbivore Interactions Structural Equation Fitting (Abundance), echo = TRUE}
## Danaus
danaus.abundance.early.urb_herb.toronto <- glm.nb(
	Danaus.early ~ Distance + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
	data = final.abundance.data
	)
danaus.abundance.late.urb_herb.toronto <- glm.nb(
	Danaus.late ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)

## Rhyssomatus
rhyssomatus.abundance.early.urb_herb.toronto <- glm.nb(
	Rhyssomatus.early ~ Distance,
  data = final.abundance.data
	)
rhyssomatus.abundance.late.urb_herb.toronto <- glm.nb(
	Rhyssomatus.late ~ Distance + Rhyssomatus.early,
  data = final.abundance.data
	)

## Aphis
aphis.abundance.early.urb_herb.toronto <- glm.nb(
	Aphis.early ~ Distance + Danaus.early + Rhyssomatus.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)
aphis.abundance.late.urb_herb.toronto <- glm.nb(
	Aphis.late ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)

## Tetraopes
tetraopes.abundance.early.urb_herb.toronto <- glm.nb(
	Tetraopes.early ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Liriomyza.early,
  data = final.abundance.data
	)
tetraopes.abundance.late.urb_herb.toronto <- glm.nb(
	Tetraopes.late ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)

## Liriomyza
liriomyza.abundance.early.urb_herb.toronto <- glm.nb(
	Liriomyza.early ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early,
  data = final.abundance.data
	)
liriomyza.abundance.late.urb_herb.toronto <- glm.nb(
	Liriomyza.late ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.abundance.data
	)
```

\vspace{10pt}

```{r Urbanization + Herbivore Interactions Structural Equation Diagnostics (Abundance), echo = TRUE}
## Check model assumptions
# Danaus abundance GLMs
check_model(danaus.abundance.early.urb_herb.toronto) # Good fit
check_model(danaus.abundance.late.urb_herb.toronto) # Good fit

# Rhyssomatus abundance GLMs
check_model(rhyssomatus.abundance.early.urb_herb.toronto) # Good fit
check_model(rhyssomatus.abundance.late.urb_herb.toronto) # Good fit

# Aphis abundance GLMs
check_model(aphis.abundance.early.urb_herb.toronto) # Good fit
#check_model(aphis.abundance.late.urb_herb.toronto) # Good fit

# Tetraopes abundance GLMs
check_model(tetraopes.abundance.early.urb_herb.toronto) # Poor fit
check_model(tetraopes.abundance.late.urb_herb.toronto) # Poor fit

# Liriomyza abundance GLMs
check_model(liriomyza.abundance.early.urb_herb.toronto) # Good fit
check_model(liriomyza.abundance.late.urb_herb.toronto) # Good fit
```



\newpage
## Urbanization (Hypothesized pSEM 1) | Presence-Absence

```{r Urbanization Structural Equation Fitting (Presence-Absence), echo = TRUE}
## Danaus
danaus.presence.absence.early.urb.toronto <- glm(
	Danaus.early ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
danaus.presence.absence.late.urb.toronto <- glm(
	Danaus.late ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Rhyssomatus
rhyssomatus.presence.absence.early.urb.toronto <- glm(
	Rhyssomatus.early ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
rhyssomatus.presence.absence.late.urb.toronto <- glm(
	Rhyssomatus.late ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Aphis
aphis.presence.absence.early.urb.toronto <- glm(
	Aphis.early ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
aphis.presence.absence.late.urb.toronto <- glm(
	Aphis.late ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Tetraopes
tetraopes.presence.absence.early.urb.toronto <- glm(
	Tetraopes.early ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
tetraopes.presence.absence.late.urb.toronto <- glm(
	Tetraopes.late ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Liriomyza
liriomyza.presence.absence.early.urb.toronto <- glm(
	Liriomyza.early ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
liriomyza.presence.absence.late.urb.toronto <- glm(
	Liriomyza.late ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
```

\vspace{10pt}

```{r Urbanization Structural Equation Diagnostics GLM (Presence-Absence), echo = TRUE}
## Check model assumptions
# Danaus presence-absence GLMs
check_model(danaus.presence.absence.early.urb.toronto) # Decent fit
check_model(danaus.presence.absence.late.urb.toronto) # Decent fit

# Rhyssomatus presence-absence GLMs
check_model(rhyssomatus.presence.absence.early.urb.toronto) # Good fit
check_model(rhyssomatus.presence.absence.late.urb.toronto) # Good fit

# Aphis presence-absence GLMs
check_model(aphis.presence.absence.early.urb.toronto) # Good fit
check_model(aphis.presence.absence.late.urb.toronto) # Good fit

# Tetraopes presence-absence GLMs
check_model(tetraopes.presence.absence.early.urb.toronto) # Poor fit
check_model(tetraopes.presence.absence.late.urb.toronto) # Poor fit

# Liriomyza presence-absence GLMs
check_model(liriomyza.presence.absence.early.urb.toronto) # Good fit
check_model(liriomyza.presence.absence.late.urb.toronto) # Good fit
```



\newpage
## Herbivore Interactions (Hypothesized pSEM 2) | Presence-Absence

```{r Herbivore Interactions Structural Equation Fitting (Presence-Absence), echo = TRUE}
## Danaus
danaus.presence.absence.early.herb.toronto <- glm(
	Danaus.early ~ Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
danaus.presence.absence.late.herb.toronto <- glm(
	Danaus.late ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Rhyssomatus
rhyssomatus.presence.absence.late.herb.toronto <- glm(
	Rhyssomatus.late ~ Rhyssomatus.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Aphis
aphis.presence.absence.early.herb.toronto <- glm(
	Aphis.early ~ Danaus.early + Rhyssomatus.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
aphis.presence.absence.late.herb.toronto <- glm(
	Aphis.late ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Tetraopes
tetraopes.presence.absence.early.herb.toronto <- glm(
	Tetraopes.early ~ Danaus.early + Rhyssomatus.early + Aphis.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
tetraopes.presence.absence.late.herb.toronto <- glm(
	Tetraopes.late ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Liriomyza
liriomyza.presence.absence.early.herb.toronto <- glm(
	Liriomyza.early ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
liriomyza.presence.absence.late.herb.toronto <- glm(
	Liriomyza.late ~ Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
```

\vspace{10pt}

```{r Herbivore Interactions Structural Equation Diagnostics (Presence-Absence), echo = TRUE, eval = FALSE}
## Check model assumptions
# Danaus presence-absence GLMs
check_model(danaus.presence.absence.early.herb.toronto) # Decent fit
check_model(danaus.presence.absence.late.herb.toronto) # Good fit

# Rhyssomatus presence-absence GLMs
check_model(rhyssomatus.presence.absence.late.herb.toronto) # Good fit

# Aphis presence-absence GLMs
check_model(aphis.presence.absence.early.herb.toronto) # Good fit
check_model(aphis.presence.absence.late.herb.toronto) # Good fit

# Tetraopes presence-absence GLMs
check_model(tetraopes.presence.absence.early.herb.toronto) # Poor fit
check_model(tetraopes.presence.absence.late.herb.toronto) # Poor fit

# Liriomyza presence-absence GLMs
check_model(liriomyza.presence.absence.early.herb.toronto) # Good fit
check_model(liriomyza.presence.absence.late.herb.toronto) # Good fit
```



\newpage
## Urbanization & Herbivore Interactions (Hypothesized pSEM3 ) | Presence-Absence

```{r Urbanization + Herbivore Interactions Structural Equation Fitting (Presence-Absence), echo = TRUE}
## Danaus
danaus.presence.absence.early.urb_herb.toronto <- glm(
	Danaus.early ~ Distance + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
danaus.presence.absence.late.urb_herb.toronto <- glm(
	Danaus.late ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Rhyssomatus
rhyssomatus.presence.absence.early.urb_herb.toronto <- glm(
	Rhyssomatus.early ~ Distance,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
rhyssomatus.presence.absence.late.urb_herb.toronto <- glm(
	Rhyssomatus.late ~ Distance + Rhyssomatus.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Aphis
aphis.presence.absence.early.urb_herb.toronto <- glm(
	Aphis.early ~ Distance + Danaus.early + Rhyssomatus.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
aphis.presence.absence.late.urb_herb.toronto <- glm(
	Aphis.late ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Tetraopes
tetraopes.presence.absence.early.urb_herb.toronto <- glm(
	Tetraopes.early ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
tetraopes.presence.absence.late.urb_herb.toronto <- glm(
	Tetraopes.late ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)

## Liriomyza
liriomyza.presence.absence.early.urb_herb.toronto <- glm(
	Liriomyza.early ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
liriomyza.presence.absence.late.urb_herb.toronto <- glm(
	Liriomyza.late ~ Distance + Danaus.early + Rhyssomatus.early + Aphis.early + Tetraopes.early + Liriomyza.early,
  data = final.presence.absence.data,
  family = binomial(link = "logit")
	)
```

\vspace{10pt}

```{r Urbanization + Herbivore Interactions Structural Equation Diagnostics (Presence-Absence), echo = TRUE, eval = FALSE}
## Check model assumptions
# Danaus presence-absence GLMs
check_model(danaus.presence.absence.early.urb_herb.toronto) # Good fit
check_model(danaus.presence.absence.late.urb_herb.toronto) # Good fit

# Rhyssomatus presence-absence GLMs
check_model(rhyssomatus.presence.absence.early.urb_herb.toronto) # Good fit
check_model(rhyssomatus.presence.absence.late.urb_herb.toronto) # Good fit

# Aphis presence-absence GLMs
check_model(aphis.presence.absence.early.urb_herb.toronto) # Good fit
check_model(aphis.presence.absence.late.urb_herb.toronto) # Good fit

# Tetraopes presence-absence GLMs
check_model(tetraopes.presence.absence.early.urb_herb.toronto) # Decent fit
check_model(tetraopes.presence.absence.late.urb_herb.toronto) # Poor fit

# Liriomyza presence-absence GLMs
check_model(liriomyza.presence.absence.early.urb_herb.toronto) # Good fit
check_model(liriomyza.presence.absence.late.urb_herb.toronto) # Good fit
```





\newpage
# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>% 
  as.data.frame(.) %>% 
  filter(attached == TRUE) %>% 
  dplyr::select(loadedversion, date) %>% 
  rownames_to_column

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages, 
  booktabs = TRUE,
  caption = "Packages for data management and analyses."
  ) %>%
	kable_styling(
		full_width = FALSE,
  	latex_options = c("HOLD_position", "striped")
  	) 
```






```{r Save the Workspace, include = FALSE}
save.image("data_analysis/2-pSEM_checking/pSEM_checking-workspace.RData")
```




